{\helveticaitalic{Supplementary Material}}:\\ \helvetica{ Benchmarking neuromorphic systems with Nengo}

### 2015-07-28 paper/paper.tex
Incorporate feedback from Chris, part 2

\usepackage{url,lineno}
\linenumbers
\usepackage{inconsolata}
\usepackage{listings}
\lstset{language=Python}
\lstset{basicstyle=\ttfamily,breaklines=true}

@@

  Nengo is a software package for designing and simulating
  large-scale neural models.
  Nengo is architected such that the same Nengo model
  can be simulated on any of several
  Nengo backends with few to no modifications.
  Backends translate a model to specific platforms,
  which include GPUs and neuromorphic hardware.
  Nengo also contains a large test suite
  that can be run with any backend
  and focuses primarily on functional performance.
  We propose that Nengo's large test suite
  can be used to benchmark neuromorphic hardware's
  functional performance and speed simulating
  in an efficient, unbiased, and future-proof manner.
  We implement four benchmark models and show that
  Nengo can collect several benchmark metrics
  that identify situations in which
  some backends perform differently
  or significantly faster than others.

@@

The primary abstraction in Nengo is the \textit{Ensemble},
which is a group of neurons.
The activity of these neurons
forms a distributed representation of a numerical vector;
for example, a group of 100 neurons might represent
a three-dimensional vector,
and as that vector changes,
the pattern of neural activity
will change accordingly.
Two parameters are mandatory: the number of neurons,
and the dimensionality of the vector being represented.
There are several optional parameters that
affect how the neurons represent the vector space;
encoders map the vector space into currents
to be injected in the neurons,
maximum firing rates can be specified for each neuron,
the type of neuron model can be specified,
and so on.

@@

An example script showing how Nengo can
express a functional network
with 500 neurons and 6 connections
(representing 50,000 connection weights
and 100 direct current injection sites)
in under 20 lines of code
can be seen in Appendix~\ref{App:01}.

@@

Unlike traditional software testing,
there can be significant variability
in many aspects of a Nengo model.
Many model parameters, for example,
can be randomly generated;
other aspects of a model,
such as injected noise,
are necessarily random.
Noise is a fundamental property
of neuromorphic systems.
The accuracy of any large-scale model
is dependent on many factors,
including the number of neurons used
to implement a particular task.
For this reason,
functional tests can only
ensure that the backend implements
the system described by the frontend
well enough.
Each test must determine what
``well enough'' means for that particular network.
While this introduces some subjectivity
to testing,
we believe this is an acceptable consequence
of the breadth of their application.
When adapting these functional tests for benchmarking,
we record the actual accuracy rather than
ensuring that it is within some tolerances.

Nengo's test suite employs the \texttt{pytest}
testing framework \footnote{Available at \url{http://pytest.org/}.}.
\texttt{pytest} enables
expressive testing of pluggable components
(such as backends)
through what are called ``test fixtures.''
Fixtures are exposed to the test suite
as arguments that can be provided
to any test function.
\texttt{pytest} inspects the function signature,
and passes an appropriate value
to the function.
This allows for boilerplate code
to be specified once,
and run for any test that might use it.
The example script in Appendix~\ref{App:01}
demonstrates how these fixtures
look in test scripts.

@@

Each test has several parameters
that can be varied
in order to benchmark extreme cases
(see Appendix~\ref{App:01} for examples).
We test each model with parameters
typically used in large-scale models,
but make these parameterized models
available at \url{https://github.com/tbekolay/fnme2015}
for those who want to explore extreme cases.

@@

All benchmarks were run on a server
running Debian unstable.
The server was configured with
two Intel Xeon E5-2650 CPUs
clocked at 2.00GHz,
four Nvidia Tesla C2075 GPUs,
and 64 GB of RAM.
A single 48-chip SpiNN-5 board
was connected through
a 1 GB ethernet port on
the Supermicro X9DRG-QF motherboard.

@@

Figure~\ref{fig:01} gives accuracy results
for each backend on the chained communication channel model.
The boxplot shows that all five backends can
implement this model accurately,
despite five sources of potential noise.

@@

Above and beyond the benchmarking results,
however, we believe that the primary contribution
of this study is to provide evidence that Nengo
has a tested, stable, productive frontend
that can target multiple backends,
and therefore provides a platform
for benchmarking neuromorphic backends,
and other neural simulators.
While this is similar to the goal
of other projects, most notably PyNN \citep{davison2008},
Nengo is unique in focusing on
large-scale functional simulations,
rather than attempting to support
detailed single-neuron models
(though this capability is still possible in Nengo).
Topographica \citep{bednar2009} plays a similar role,
in that it can interact with multiple neural simulators
with a high-level API, but its API focuses specifically
on models of topographic maps
and other sensory pathways,
rather than focusing on function and dynamics.

While we cannot claim that Nengo
solves all of complications that arise
in benchmarking,
we believe that it improves upon
the three major issues identified in the introduction.
First, benchmarking neuromorphic hardware
with Nengo is less biased than
hardware-specific benchmarks,
because the purpose of Nengo is
to make functionally interesting large-scale models.
These models are typically built and tested
in the reference backend,
leaving little opportunity to introduce
hardware-specific optimizations
that can bias benchmarks.

@@

The authors of this paper
are three of the seven co-founders
of Applied Brain Research (ABR),
who are the sole copyright holders
of Nengo and the distilled backend.
While ABR reserves the right
to commercialize Nengo,
it is freely available
for all non-commercial purposes.
As of the writing of this paper,
ABR has not sold any licenses to Nengo,
but has used it
for other revenue-generating projects.

@@

We thank Andrew Mundy for his help
running the SpiNNaker backend
and providing feedback on drafts of this paper.
We thank Jan Gosmann for the initial version
of the product benchmark models,
and for conceptualization and implementation
of the \texttt{analytics} and \texttt{analytics\_data}
fixtures.
We thank Xuan Choo for administering
the server on which the benchmarks were run,
Eric Hunsberger for help in running
the benchmarks on the OpenCL backend,
and James Bergstra for
implementing most of the OpenCL backend.

\paragraph{Funding\textcolon}
NSERC Discovery,
NSERC Graduate Fellowships,
ONR (N000141310419)
and AFOSR (FA8655-13-1-3084). ??? Chris, can you confirm?

@@

\begin{figure}[!ht]
\begin{center}
  \includegraphics[width=85mm]{fig4}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:04} Figure \arabic{figure}.}
       {Basal Ganglia sequence model. (A) One example instance
         of the model run on the reference backend; the similarity between
         the current representation in working memory and the six possible
         actions is shown (note that in the full benchmark, ten items are
         used). The model quickly progresses from one action to the next,
         cycling back at the end of the six items. The point at which the
         model switches from selecting one action to another action
         (the transition times) are indicated with dashed grey lines.
         (B) The aggregated accuracy results for each backend on the
         basal ganglia sequence model, with all passthrough nodes included.
         The observed metric is the mean
         time to transition from one action to the next. The model is run
         for four seconds, allowing for approximately 90 transitions, depending
         on the transition time. The box shows the median and
         inter-quartile range, while the whiskers extend to 1.5 times the
         inter-quartile range; outliers are not shown.
         (C) The aggregated accuracy results for each backend on the
         basal ganglia sequence model, with most passthrough nodes pruned.
         Lines has the same meaning as in B.}
\end{figure}

\begin{figure}[!ht]
\begin{center}
  \includegraphics[width=85mm]{fig5}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:05} Figure \arabic{figure}.}
       {Build time for each model on each backend. Each bar represents
         the mean build time across 50 instances of each model;
         error bars are bootstrapped 95\% confidence intervals.}
\end{figure}

\begin{figure}[!ht]
\begin{center}
  \includegraphics[width=85mm]{fig6}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:06} Figure \arabic{figure}.}
       {Run speed for each model on each backend. Each bar represents
         the mean run speed across 50 instances of each model;
         error bars are bootstrapped 95\% confidence intervals.
         Run speed is measured as the simulation time plus overhead,
         relative to real time; e.g., a value of two indicates that
         the calling \texttt{run} for a number of seconds takes
         the model two times that number of real seconds to complete the
         \texttt{run} call.}

@@

\clearpage
\appendix

\section{Chained communication channel model}
\label{App:01}

\begin{lstlisting}
import numpy as np
import nengo
from nengo.utils.numpy import rmse

def test_cchannelchain(Simulator, analytics, plt, rng, seed):
    # Parameters that can be varied to investigate extreme cases
    dims = 2
    layers = 5
    n_neurons = 100
    synapse = nengo.Lowpass(0.01)

    with nengo.Network(seed=seed) as model:
        hypersphere = nengo.dists.UniformHypersphere()
        value = hypersphere.sample(dims, 1, rng=rng).ravel()
        stim = nengo.Node(value)

        ens = [nengo.Ensemble(n_neurons, dimensions=dims)
               for _ in range(layers)]

        nengo.Connection(stim, ens[0])
        for i in range(layers - 1):
            nengo.Connection(ens[i], ens[i+1], synapse=synapse)

        p_input = nengo.Probe(stim)
        p_outputs = [nengo.Probe(ens[i], synapse=synapse)
                     for i in range(layers)]

    sim = Simulator(model)
    sim.run(0.5)

    for p_output in p_outputs:
        plt.plot(sim.trange(), sim.data[p_output])
    plt.plot(sim.trange(), sim.data[p_input], color='k', linewidth=1)
    plt.ylabel('Decoded output')
    plt.xlabel('Time (s)')

    last = p_outputs[-1]
    decoding_rmse = rmse(value, sim.data[last][sim.trange() > 0.4]
    analytics.add_data('rmse', decoding_rmse)

def test_compare_cchannelchain(analytics_data, plt):
    rmses = [d['rmse'] for d in analytics_data]
    plt.bar(np.arange(len(rmses)), rmses, align='center')
    plt.ylabel("RMSE")
\end{lstlisting}

>>>>

\usepackage{url,lineno}
\linenumbers
\usepackage{inconsolata}

@@

  Nengo is a software package for designing and simulating
  large-scale neural models.
  Nengo is architected such that the same Nengo model
  can be simulated on any of several
  Nengo backends with few to no modifications.
  Backends translate a model to specific platforms,
  which include GPUs and neuromorphic hardware.
  Nengo also contains a large test suite
  that can be run with any backend
  and focuses primarily on functional performance.
  We propose that Nengo's large test suite
  can be used to benchmark neuromorphic hardware's
  functional performance and simulation speed
  in an efficient, unbiased, and future-proof manner.
  We implement four benchmark models and show that
  Nengo can collect several benchmark metrics
  across five different backends
  that identify situations in which
  some backends perform
  with different accuracy and speed.

@@

The primary abstraction in Nengo is the \textit{Ensemble},
which is a group of neurons.
The activity of these neurons
is generally taken to be
a distributed representation
of a numerical state vector;
for example, a group of 100 neurons might represent
a three-dimensional vector,
and as that vector changes,
the pattern of neural activity
will change accordingly.
Two parameters are mandatory: the number of neurons,
and the dimensionality of the vector being represented.
There are several optional parameters that
affect how the neurons represent the vector space;
encoders map the vector space into currents
to be injected in the neurons,
maximum firing rates can be specified for each neuron,
the type of neuron model can be specified,
and so on.

@@

An example script showing how Nengo can
express a functional network
with 500 neurons and 6 connections
(representing 50,000 connection weights
and 100 direct current injection sites)
in under 20 lines of code
can be seen in Supplementary Figure~2.

It is important to note that,
although the Nengo frontend
is designed to make functional networks
with compact code,
any spiking neural network topology
can be implemented in Nengo.
While we will only show examples
of functional connection between ensembles,
it is also possible
to make direct neuron-to-neuron connections;
functional and direct connections
can coexist in the same network,
as is commonly done in situations
requiring direct inhibitory currents.

@@

Unlike traditional software testing,
there can be significant variability
in many aspects of a Nengo model.
Many model parameters, for example,
can be randomly generated;
other aspects of a model,
such as injected noise,
are necessarily random.
Noise is a fundamental property
of neuromorphic systems.
The accuracy of any large-scale model
is dependent on many factors,
including the number of neurons used
to implement a particular task.
For this reason,
functional tests can only
ensure that the backend implements
the system described by the frontend
well enough.
Each test must determine what
``well enough'' means for that particular network.
While this introduces some subjectivity
to testing,
we believe this is an acceptable consequence
of being able to test across multiple backends.
When adapting these functional tests for benchmarking,
we record the actual accuracy rather than
ensuring that it is within some tolerances.

Nengo's test suite employs the \texttt{pytest}
testing framework.\footnote{Available at \url{http://pytest.org/}.}
\texttt{pytest} enables
expressive testing of pluggable components
(such as backends)
through what are called ``test fixtures.''
Fixtures are exposed to the test suite
as arguments that can be provided
to any test function.
\texttt{pytest} inspects the function signature,
and passes an appropriate value
to the function.
This allows for boilerplate code
to be specified once,
and run for any test that might use it.
A demonstration of how these fixtures
are used in test scripts
can be seen in an example script,
included as Supplementary Figure~2.

@@

Each test has several parameters
that can be varied
in order to benchmark a wide variety of cases
(see Appendix~\ref{App:01} for examples).
We test each model with parameters
typically used in large-scale models,
but make these parameterized models
available at \url{https://github.com/ctn-archive/bekolay-fnme2015}
for those who want to explore additional cases.

@@

All benchmarks were run on a server
running Debian sid.
The server was configured with
two Intel Xeon E5-2650 CPUs
clocked at 2.00GHz,
four Nvidia Tesla C2075 GPUs,
and 64 GB of RAM.
A single 48-chip SpiNN-5 board
was connected through
a 1 GB ethernet port on
the Supermicro X9DRG-QF motherboard
for the SpiNNaker benchmarks.

@@

Figure~\ref{fig:01} gives accuracy results
for each backend on the chained communication channel model.
The boxplot shows that all five backends can
implement this model accurately,
despite five layers of processing that include noise.

@@

Above and beyond the benchmarking results,
however, we believe that the primary contribution
of this study is to provide evidence that Nengo
has a tested, stable, productive frontend
that can target multiple backends,
and therefore provides a platform
for benchmarking neuromorphic backends,
and other neural simulators.
While this is similar to the goal
of other projects, most notably PyNN \citep{davison2008},
Nengo is unique in focusing on
large-scale functional simulations,
rather than attempting to support
detailed single-neuron models
(though this capability is still possible in Nengo).
Topographica \citep{bednar2009} plays a similar role,
in that it can interact with multiple neural simulators
with a high-level API, but its API focuses specifically
on models of topographic maps
and other sensory pathways,
rather than focusing on
a wider variety of functions
and dynamics more generally.

While we cannot claim that Nengo
solves all of the complications that arise
in benchmarking,
we believe that it improves upon
the three major issues identified in the introduction.
First, benchmarking neuromorphic hardware
with Nengo is less biased than
hardware-specific benchmarks,
because the purpose of Nengo is
to make functionally interesting large-scale models.
These models are typically built and tested
in the reference backend,
leaving little opportunity to introduce
hardware-specific optimizations
that can bias benchmarks.

@@

The authors of this paper
are three of the seven co-founders
of Applied Brain Research (ABR, Inc.),
which is the sole copyright holder
of Nengo and the distilled backend.
While ABR reserves the right
to commercialize Nengo,
it is freely available
for all non-commercial purposes.
As of the writing of this paper,
ABR has not sold any licenses to Nengo,
but has used it
for other revenue-generating projects.

@@

We thank Andrew Mundy for his help
running the SpiNNaker backend
and providing feedback on drafts of this paper.
We thank Jan Gosmann for the initial version
of the product benchmark models,
and for conceptualization and implementation
of the \texttt{analytics} and \texttt{analytics\_data}
fixtures.
We thank Xuan Choo for administering
the server on which the benchmarks were run,
Eric Hunsberger for help in running
the benchmarks on the OpenCL backend,
and James Bergstra for
implementing most of the OpenCL backend.
We thank the Brainstorm group
at Stanford University for making
their experimental hardware emulation backend
available to us.

\paragraph{Funding\textcolon}
NSERC Graduate Fellowships,
NSERC Discovery (grant 261453),
ONR (N000141310419)
AFOSR (FA8655-13-1-3084),
Canada Research Chairs,
and Canadian Foundation for Innovation
Ontario Innovation Trust.

@@

\begin{figure}[!ht]
\begin{center}
  \includegraphics[width=85mm]{fig4}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:04} Figure \arabic{figure}.}
       {Basal Ganglia sequence model. (A) One example instance
         of the model run on the reference backend; the similarity between
         the current representation in working memory and the six possible
         actions is shown (note that in the full benchmark, ten items are
         used). The model quickly progresses from one action to the next,
         cycling back at the end of the six items. The point at which the
         model switches from selecting one action to another action
         (the transition times) are indicated with dashed grey lines.
         (B) The aggregated accuracy results for each backend on the
         basal ganglia sequence model, with all passthrough nodes included.
         The observed metric is the mean
         time to transition from one action to the next. The model is run
         for four seconds, allowing for approximately 90 transitions, depending
         on the transition time. The box shows the median and
         inter-quartile range, while the whiskers extend to 1.5 times the
         inter-quartile range; outliers are not shown.
         (C) The aggregated accuracy results for each backend on the
         basal ganglia sequence model, with most passthrough nodes pruned.
         Lines have the same meaning as in B.}
\end{figure}

\begin{figure}[!ht]
\begin{center}
  \includegraphics[width=85mm]{fig5}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:05} Figure \arabic{figure}.}
       {Build time for each model on each backend. Each bar represents
         the mean build time across 50 instances of each model;
         error bars are bootstrapped 95\% confidence intervals.
         BG Sequence * refers to the basal ganglia sequence model
         in which passthrough nodes have been removed.}
\end{figure}

\begin{figure}[!ht]
\begin{center}
  \includegraphics[width=85mm]{fig6}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:06} Figure \arabic{figure}.}
       {Run speed for each model on each backend. Each bar represents
         the mean run speed across 50 instances of each model;
         error bars are bootstrapped 95\% confidence intervals.
         Run speed is measured as the simulation time plus overhead,
         relative to real time; e.g., a value of two indicates that
         the calling \texttt{run} for a number of seconds takes
         the model two times that number of real seconds to complete the
         \texttt{run} call.
         BG Sequence * refers to the basal ganglia sequence model
         in which passthrough nodes have been removed.}

@@

### 2015-07-28 paper/supplementary.tex
Incorporate feedback from Chris, part 2

%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
\documentclass{frontiers_suppmat} % for all articles

\usepackage{url}

@@

\def\articleType{Supplementary Material}
\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Bekolay {et~al.}}
\def\Authors{Trevor Bekolay\,$^{1,*}$,
  Terrence C. Stewart\,$^{1}$,
  Eric Hunsberger\,$^1$,
  Andrew Mundy\,$^2$ and
  Chris Eliasmith\,$^1$}
\def\Address{$^{1}$Centre for Theoretical Neuroscience,
  University of Waterloo,
  Waterloo, ON, Canada\\
  $^{2}$ Advanced Processors Technologies Research Group,
  School of Computer Science,
  University of Manchester,
  Manchester, UK}
\def\corrAuthor{Trevor Bekolay}
\def\corrAddress{Centre for Theoretical Neuroscience,
  David R. Cheriton School of Computer Science,
  University of Waterloo,
  200 University Avenue West,
  Waterloo, ON  N2L~3G1, Canada}
\def\corrEmail{tbekolay@uwaterloo.ca}

% \color{FrontiersColor} Is the color used in the Journal name, in the title, and the names of the sections.

@@

\begin{figure}[!ht]
\begin{center}
  \includegraphics[width=85mm]{fig7}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:01} Supplementary Figure \arabic{figure}.}
       {Run time for each model with probes removed on each backend.
         Each bar represents the mean run time across 100 instances
         of each model;
         error bars are 95\% confidence intervals.
         Run time is measured relative to real time;
         e.g., a value of two indicates that the model ran twice as slow
         as real time.}
\end{figure}

>>>>

\documentclass{frontiers_suppmat} % for all articles

\usepackage{url}
\usepackage{inconsolata}
\usepackage{listings}
\lstset{language=Python}
\lstset{basicstyle=\ttfamily,breaklines=true}

@@

\def\articleType{Supplementary Material}
\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Bekolay {et~al.}}
\def\Authors{Trevor Bekolay\,$^{1,*}$,
  Terrence C. Stewart\,$^{1}$, and
  Chris Eliasmith\,$^1$}
\def\Address{$^{1}$Centre for Theoretical Neuroscience,
  University of Waterloo,
  Waterloo, ON, Canada}
\def\corrAuthor{Trevor Bekolay}
\def\corrAddress{Centre for Theoretical Neuroscience,
  David R. Cheriton School of Computer Science,
  University of Waterloo,
  200 University Avenue West,
  Waterloo, ON  N2L~3G1, Canada}
\def\corrEmail{tbekolay@uwaterloo.ca}

@@

\begin{table}[!ht]
\textbf{\refstepcounter{table}\label{Tab:01} Supplementary Table \arabic{table}.}{
  Software versions used for benchmarking.
  The PyPI name is the unique identifier used for installing the Python package
  through the Python Package Index (PyPI). Packages can be found by
  visiting \url{https://pypi.python.org/pypi/<PyPI name>}.}

\processtable{ }
{\begin{tabular}{lcc}\toprule
 Package & PyPI name & Version number\\\midrule
 Nengo & \texttt{nengo} & Development version, commit \texttt{7d2d24145} \\
 Distilled backend & \texttt{nengo\_distilled} & 0.1.0 \\
 OpenCL backend & \texttt{nengo\_ocl} & 0.1.0 \\
 Brainstorm backend & Not available on PyPI & Development version, commit \texttt{ac3cfa708} \\
 SpiNNaker backend & \texttt{nengo\_spinnaker} & 0.2.4 \\
 NumPy & \texttt{numpy} & 1.8.1 \\\botrule
\end{tabular}}{}
\end{table}

\begin{figure}[!ht]
\begin{center}
  \includegraphics[width=180mm]{fig7}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:01} Supplementary Figure \arabic{figure}.}
       {Run time for each model with probes removed on each backend.
         Each bar represents the mean run time across 100 instances
         of each model;
         error bars are 95\% confidence intervals.
         Run time is measured relative to real time;
         e.g., a value of two indicates that the model ran twice as slow
         as real time.
         BG Sequence * refers to the basal ganglia sequence model
         in which passthrough nodes have been removed.}
\end{figure}

\begin{figure}[!ht]
\begin{lstlisting}
import numpy as np
import nengo
from nengo.utils.numpy import rmse

def test_cchannelchain(Simulator, analytics, plt, rng, seed):
    # Parameters that can be varied to investigate extreme cases
    dims = 2
    layers = 5
    n_neurons = 100
    synapse = nengo.Lowpass(0.01)

    with nengo.Network(seed=seed) as model:
        hypersphere = nengo.dists.UniformHypersphere()
        value = hypersphere.sample(dims, 1, rng=rng).ravel()
        stim = nengo.Node(value)

        ens = [nengo.Ensemble(n_neurons, dimensions=dims)
               for _ in range(layers)]

        nengo.Connection(stim, ens[0])
        for i in range(layers - 1):
            nengo.Connection(ens[i], ens[i+1], synapse=synapse)

        p_input = nengo.Probe(stim)
        p_outputs = [nengo.Probe(ens[i], synapse=synapse)
                     for i in range(layers)]

    sim = Simulator(model)
    sim.run(0.5)

    for p_output in p_outputs:
        plt.plot(sim.trange(), sim.data[p_output])
    plt.plot(sim.trange(), sim.data[p_input], color='k', linewidth=1)
    plt.ylabel('Decoded output')
    plt.xlabel('Time (s)')

    last = p_outputs[-1]
    decoding_rmse = rmse(value, sim.data[last][sim.trange() > 0.4]
    analytics.add_data('rmse', decoding_rmse)

def test_compare_cchannelchain(analytics_data, plt):
    rmses = [d['rmse'] for d in analytics_data]
    plt.bar(np.arange(len(rmses)), rmses, align='center')
    plt.ylabel("RMSE")
\end{lstlisting}
\textbf{\refstepcounter{figure}\label{fig:02} Supplementary Figure \arabic{figure}.}
       {Python code for implementing the chained communication channel model.}
\end{figure}
